\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begin{thebibliography}{25}
    \bibitem{1} Документация QMK: электронно-библиотечная система: сайт. -- URL: https://docs.qmk.fm (дата обращения: 15.03.2023).
    \bibitem{2} Документация Vial-QMK: электронно-библиотечная система: сайт. -- URL: https://get.vial.today/docs/index.html (дата обращения: 16.03.2023).
    \bibitem{3} Krzychowski, Patryk. Practical Programming with Arduino and ESP32: A Beginner’s Guide to Building Real-World Projects. Packt Publishing Ltd, 2021. 310 p. ISBN 978-1-80181-648-9. -- Текст: непосредственный.
    \bibitem{4} Liu, Alex. Getting Started with Arduino: An Introduction to Physical Computing. Maker Media Inc, 2021. 184 p. ISBN 978-1-68045-546-5. -- Текст: непосредственный.
    \bibitem{5} O’Sullivan, Brian. Learn Arduino Programming: With Circuit Diagrams and Explanations. John Wiley \& Sons, 2020. 288 p. ISBN 978-1-119-67574-8. -- Текст: непосредственный.
    \bibitem{6} Blinkenlights Forum: электронно-библиотечная система: сайт. -- URL: https://geekhack.org/index.php?board=13.0 (дата обращения: 17.03.2023).
    \bibitem{7} Heinemann, Philip. Modern C++ Concurrency in Action: Ownership-Based Memory Management. Manning Publications Co, 2022. 368 p. ISBN 978-1-61729-868-3. -- Текст: непосредственный.
    \bibitem{8} Docs.CircuitPython: электронно-библиотечная система: сайт. -- URL: https://circuitpython.readthedocs.io/en/latest/sharedbindings/pulseio/PulseIn.html (дата обращения: 18.03.2023).
    \bibitem{9} Kingman, James. Advanced Arduino Development: Exploring Techniques for High-Performance IoT Solutions. Apress, 2021. 240 p. ISBN 978-1-4842-6842-3. -- Текст: непосредственный.
    \bibitem{10} Dokter, Adam. Hacking Arduino: Learning Electronics with Experiments and Code. No Starch Press, 2021. 352 p. ISBN 978-1-7185-0112-4. -- Текст: непосредственный.
    \bibitem{11} Hackerboards: электронно-библиотечная система: сайт. -- URL: http://hackerboards.com/forums/viewforum.php?id=3 (дата обращения: 19.03.2023).
    \bibitem{12} Official Arduino Documentation: электронно-библиотечная система: сайт. -- URL: https://www.arduino.cc/reference/en/language/functions/io/digital/digitalread (дата обращения: 20.03.2023).
    \bibitem{13} DataSheet NXP LPC11U24: электронно-библиотечная система: сайт. -- URL: https://www.nxp.com/docs/en/data-sheet/LPC11U2X.pdf (дата обращения: 21.03.2023).
    \bibitem{14} Arduino UNO Reference: электронно-библиотечная система: сайт. -- URL: https://store.arduino.cc/products/arduino-uno-rev3 (дата обращения: 22.03.2023).
    \bibitem{15} Banzi, Massimo. Getting Started with Arduino: The Open Source Electronics Prototyping Platform. Maker Media Inc, 2014. 150 p. ISBN 978-1-4493-6518-0. -- Текст: непосредственный.
    \bibitem{16} Knight, Bill. Microcontroller Fundamentals for Engineers and Scientists. Elsevier Science, 2021. 432 p. ISBN 978-0-12-823636-6. -- Текст: непосредственный.
    \bibitem{17} Документация ESP-IDF для ESP32: электронно-библиотечная система: сайт. -- URL: https://docs.espressif.com/projects/esp-idf/en/latest/esp32/apireference/system/wifi.html (дата обращения: 23.03.2023).
    \bibitem{18} Wallace, Jeff. Essential Microprocessors: Designing Low-Power Embedded Systems. McGraw-Hill Education, 2020. 480 p. ISBN 978-1-260-45846-8. -- Текст: непосредственный.
    \bibitem{19} How to Use Arduino Leonardo Board: электронно-библиотечная система: сайт. -- URL: https://create.arduino.cc/projecthub/karanpandey25/using-arduino-leonardo-d56700 (дата обращения: 24.03.2023).
    \bibitem{20} Upton, Eben. The MagPi Magazine Issue 86: Introductory Guide to DIY Electronics. Raspberry Pi Foundation, 2020. 128 p. ISBN 978-1-913581-03-7. -- Текст: непосредственный.
    \bibitem{21} Westfall, Dave. Mastering Microprocessor Design: Principles and Practices. CRC Press, 2021. 512 p. ISBN 978-0-367-61028-8. -- Текст: непосредственный.
    \bibitem{22} Jackson, Aaron. Arduino Blueprints: Expert Recipes for Creating Simple to Complex Projects. Packt Publishing Ltd, 2020. 304 p. ISBN 978-1-83898-322-9. -- Текст: непосредственный.
    \bibitem{23} Davis, Stephen. Arduino Cookbook: Recipes for Everyday Problems Solving. O’Reilly Media, Inc., 2021. 560 p. ISBN 978-1-4920-7558-6. -- Текст: непосредственный.
    \bibitem{24} The Ultimate Guide to Customizing Your Keyboard: электронно-библиотечная система: сайт. -- URL: https://deskthority.net/wiki/Main\_Page (дата обращения: 25.03.2023).
    \bibitem{25} Nelson, Matthew. Beginning Arduino: Programming and Problem Solving. Apress, 2021. 320 p. ISBN 978-1-4842-6667-4. -- Текст: непосредственный.
    
\end{thebibliography}
